BarnebyLives: an R package to create herbarium specimen labels and clean spreadsheets

### 2025-04-16 manuscript/BarnebyLives An R package to create and qc herbarium labels.rmd
data
order of operations

associates_spell_check_veg <- system.time({ # ensure associated species are spelled correctly. 
  data <- associates_spell_check(data, 'Vegetation', p2tax)
})

@@

time_associate_dropper <- system.time({ # remove the focal taxon from the noted associates
  data <- associate_dropper(data, 'Full_name', col  = 'Associates')
})

time_associate_dropper <- system.time({ # remove the focal taxon from the noted associates
  data <- associate_dropper(data, 'Full_name', col  = 'Vegetation')
})

@@

# honestly just overwrite these too. 
data <- data %>% 
  select(-SpellCk.gGRP, -Match, -SpellCk.taxon_rank, 
        -Infrarank, -Infraspecies, -Binomial_authority, -Infraspecific_authority) |>
  rename(Full_name = SpellCk.taxon_name, Genus = SpellCk.genus, Epithet = SpellCk.species, 
         Binomial_authority = POW_Binom_authority, Infraspecific_authority = POW_Infra_authority,
         Infrarank = SpellCk.infraspecific_rank, Infraspecies = SpellCk.infraspecies) %>% 
  mutate(
    Slope = slope, 
    Aspect = aspect
  ) |>
  unite(Name_authority, 
        Genus, Epithet, Binomial_authority, Infrarank, Infraspecies, Infraspecific_authority,
        remove = F, na.rm = T, sep = ' ') |>
  sf::st_drop_geometry()

@@

raw_lab_time <- system.time({
  purrr::walk(
  .x = processed$Collection_number,
  ~ rmarkdown::render(
    input = './labels/skeleton.Rmd',
    output_file = file.path(p, glue::glue("{.x}.pdf")),
    params = list(Collection_number = {.x})
    )
  )
})

@@

```{r combine labels, eval = F}
## this SHOULD be a sh chunk, so launch in a shell! I just want to be sure you can see the code. 
## and eval = TRUE will be respected. 
user: pwd
/media/steppe/hdd/Barneby_Lives-dev/manuscript/labels/raw
# this will have both your script and a dir full of raw labels with a users name
# now launch the bash script with: 
bash render_labels.sh collector='Reed'
# or chmod it etc!
# et voila! data will be saved up on dir in a 'final' directory. 
# we timed it like this:
\time -o ../process2final.txt  bash render_labels.sh collector='Reed'
```

>>>>

time_associate_dropper <- system.time({ # remove the focal taxon from the noted associates
  data <- associate_dropper(data, 'Binomial', col  = 'Associates')
})

@@

time_associate_dropper <- system.time({ # remove the focal taxon from the noted associates
  data <- associate_dropper(data, 'Binomial', col  = 'Vegetation')
})

associates_spell_check_ass <- system.time({ # ensure associated species are spelled correctly. 
  data <- associates_spell_check(data, 'Vegetation', p2tax)
})

@@

# honestly just overwrite these too. 
data <- data %>% 
  select(-SpellCk.gGRP, -Match, -SpellCk.taxon_rank, 
        -Infrarank, -Infraspecies, -Binomial_authority, -Infraspecific_authority, -Family) |>
  rename(Full_name = SpellCk.taxon_name,
         Genus = SpellCk.genus, 
         Epithet = SpellCk.species, 
         Binomial_authority = POW_Binom_authority, 
         Infraspecific_authority = POW_Infra_authority,
         Infrarank = SpellCk.infraspecific_rank, 
         Infraspecies = SpellCk.infraspecies,
         Family = POW_Family) %>% 
  mutate(
    Slope = slope, 
    Aspect = aspect
  ) |>
  unite(Name_authority, 
        Genus, Epithet, Binomial_authority, Infrarank, Infraspecies, Infraspecific_authority,
        remove = F, na.rm = T, sep = ' ') |>
  sf::st_drop_geometry()

@@

raw_lab_time <- system.time({
  purrr::walk(
  .x = na.omit(processed$Collection_number),
  ~ rmarkdown::render(
    input = './labels/skeleton.Rmd',
    output_file = file.path(p, glue::glue("{.x}.pdf")),
    params = list(Collection_number = {.x})
    )
  )
})

@@

```{r combine labels, eval = F}
## this SHOULD be a sh chunk, so launch in a shell! I just want to be sure you can see the code. 
## and eval = TRUE will be respected. 
user: pwd
/media/steppe/hdd/Barneby_Lives-dev/manuscript/labels/raw
# this will have both your script and a dir full of raw labels with a users name
# now launch the bash script with:

# or chmod it etc!
# et voila! data will be saved up on dir in a 'final' directory. 
# we timed it like this:
\time -o ../process2final.txt  bash render_labels.sh collector='Reed'
```
